Fixing Vulnerabilities Hinders Maintainability

### 2019-01-30 paper/ICPC19/icpc19.tex
fix
adding more to intro

ISO describes software maintainability as “the degree of effectiveness and
efficiency with which a software product or system can be modified to improve
it, correct it or adapt it to changes in environment, and in requirements” on
software quality ISO/IEC 25010. ISO does not provide any specific guidelines or
formula to calculate maintainability. Thus, we resort on Software Improvement
Group’s web-based source code analysis service Better Code Hub
(BCH)~\cite{Visser:2016:OREILLY} to compute the maintainability of a given
project. BCH compiles the ISO/IEC 25010 into a set of 10 guidelines that are the
base of BCH's evaluation. Two examples of guidelines used by BCH are the
\emph{Write Simple Units of Code} based on the McCabe Complexity~\cite{1702388}
and \emph{Keep your Codebase Small} based on the idea that smaller codebases are
easier to maintain and less sensitive to defects~\cite{Visser:2016:OREILLY}.

@@

  \item An analysis of how likely energy changes need to be
  maintained, in comparison to regular commits.

>>>>

ISO describes software maintainability as ``the degree of effectiveness and
efficiency with which a software product or system can be modified to improve
it, correct it or adapt it to changes in environment, and in requirements'' on
software quality ISO/IEC 25010. As ISO does not provide any specific guidelines or
formula to calculate maintainability, we resort on Software Improvement
Group (SIG)’s web-based source code analysis service Better Code Hub
(BCH)~\cite{Visser:2016:OREILLY} to compute the maintainability of a given
project. BCH compiles the ISO/IEC 25010 into a set of 10 guidelines that are the
base of BCH's evaluation. Two examples of guidelines used by BCH are the
\emph{Write Simple Units of Code} based on the McCabe Complexity~\cite{1702388}
and \emph{Keep your Codebase Small} based on the idea that smaller codebases are
easier to maintain and less sensitive to defects~\cite{Visser:2016:OREILLY}.
Compliance to the guidelines is derived from the SIG's
industry benchmark which, according to official sources, consists of over 8
billion lines of code in more than 180 different technologies. SIG analyzes
around 15 million lines of code, per week.

@@

  \item An analysis of how likely security-related changes need to be
  maintained, in comparison to regular commits.
